Concurrent Programming in Harmony

### 2022-01-22 book/paper.tex
update installation documentation

On a command line/terminal, run \texttt{pip install harmony-model-checker}.
If you are on a Windows system, then you may encounter an error message
like \texttt{error: Microsoft Visual C++ 14.0 or greater is required...} along with a link.
If so, follow the link to install "Microsoft C++ Build Tools".

After installing Harmony, run the command \texttt{harmony} on the command line to confirm
that it is installed.

>>>>

On a command line/terminal, run \texttt{pip install harmony-model-checker}.
If you are on a Windows system, then you may encounter an error message
like \texttt{error: Microsoft Visual C++ 14.0 or greater is required...} along with a link.
If so, follow the link to install "Microsoft C++ Build Tools" and the "Desktop development with C++" workload.

After installing Harmony, run the command \texttt{harmony} on the command line to confirm
that it is successfully installed.
